---
title: "corpus_creation"
author: "Joshua Catalano"
date: "July 19, 2018"
output: html_document
---
Load the necessary libraries.

```{r}
library(tidyverse)
library(stringr)
library(tokenizers)
library(tidytext)
library(topicmodels)
library(dplyr)
library(ggplot2)
library(reshape2)
```
Import a list of stopwords.

```{r setup, include=FALSE}
# Load an improved stopwords list 

stopwords_jockers <- read_file("jockers_stop_words.txt")
stopwords_jockers <- data_frame(stopwords = str_split(stopwords_jockers, ", ")[[1]])
colnames(stopwords_jockers)[1] <- "word"

```

Create a functino to read-in a corpus.

```{r}

# Read Corpus function

read_corpus <- function(dir) {
  files <- list.files(path = dir, full.names = TRUE)
  doc_ids <- tools::file_path_sans_ext(basename(files))
  docs <- purrr::map_chr(files, readr::read_file)
  tibble::data_frame(doc_id = doc_ids,
                     filename = basename(files),
                     text = docs)
}
```

Read-in the corpus. Note: This file path should be a folder containing all of the .txt files. 

```{r}
#This is a folder of text files created from the csv_2_text_script.Rmd
sample_corpus <- read_corpus("/Users/josh/Documents/CRDH_History/CRDH_history_channel/text_files")
                             
#saveRDS(my_corpus, ".rds")
```

Filter out any potential texts with only a few words.

```{r}
#remove examples with only a few words
sample_corpus <- sample_corpus %>% 
  mutate(words = count_words(text)) 

sample_corpus <- sample_corpus %>%
  filter(words > 5)
```

Plot the texts by word length.

```{r}
ggplot(sample_corpus, aes(x = words)) + geom_histogram(binwidth = 5) +
  labs(title = "Lengths of Texts")
```

A function to allow you to easily read the text of a particular document. 

```{r}

#A function to read the document NEEDS TO BE MODIFIED FOR IDS
read_doc <- function(id) {
  out <- sample_corpus %>% 
    filter(filename == id)
  cat(out[["text"]])
}
```

Tokenize the Corpus

Create a tokenized corpus to examine word counts. 

```{r}

#Tokenize the Corpus

tokenized_corpus <- sample_corpus %>% 
  select(filename, text) %>% 
  unnest_tokens(word, text, token = "words")

word_counts <- tokenized_corpus %>% 
  count(word, sort = TRUE)


```

Prune the vocabulary to remove outliers, proper names, and words specific to the corpus that may throw off the topic models.

```{r}
#Pruning the vocabulary to remove outliers, proper names, and words specific to the corpus that may throw off the topic models.

# Words to drop by frequency
words_to_drop <- word_counts %>% 
  filter(n <= 2 | n >= 10000) 

# Filter out specific words
words_to_drop_2 <- c("chumlee, chum, frank's, chum's, rip, rip's, troy, pawn, guys, stars, rick's, shop, dwaine, las, da, it's, he's, episode, bear, chase, seen, count's, count, kustoms, cold, deal")

words_to_drop_2 <- data_frame(stopwords = str_split(words_to_drop_2, ", ")[[1]])
colnames(words_to_drop_2)[1] <- "word"

words_to_drop_2 <- as.data.frame(words_to_drop_2)
names(words_to_drop_2)[1]<-"word"

nrow(words_to_drop) / nrow(word_counts)
```

Dropping words by frequency and stopwords. 

```{r}

# Drop words by frequency and also stopwords

tokenized_corpus<- tokenized_corpus%>% 
  anti_join(words_to_drop, by = "word") %>% 
  anti_join(stopwords_jockers, by = "word") %>%
  anti_join(words_to_drop_2, by = "word")
```

Create a fucntion to plot words. 

```{r}
#Plot words funtion

plot_words <- function(tidy_df, n = 10) {
  require(ggplot2)
  require(dplyr)
  tidy_df %>%
    count(word, sort = TRUE) %>%
    top_n(n = n, n) %>% 
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col() +
    xlab(NULL) +
    coord_flip()
}
```

Plot the tokenized corpus.

```{r}
plot_words(tokenized_corpus, n = 60)
```

Create figure 2.

```{r}
figure_2 <- tokenized_corpus %>%
  count(word, sort = TRUE) %>%
    top_n(60, n) %>% 
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col(fill = "dark green") +
    labs(title = "Most Common Words Included in History Episode Descriptions", subtitle = "*Pruned vocab not included | each episode only included once", y = "Word Count") +
    ylab("Word Count") +
    xlab("Word") +
    theme(plot.title = element_text(hjust = 0.5, size =18)) +
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    theme(axis.title.y = element_text(size = 16)) +
    theme(axis.title.x = element_text(size = 16)) +
    theme(axis.title.x = element_text(margin = margin(t = 12, r = 00, b = 10, l = 0))) +
    theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 12))) +
    theme(plot.title = element_text(margin = margin(t = 15, r = 00, b = 8, l = 0))) +
    coord_flip()
```


```{r}
# TO SAVE PNG FILE
 ggsave("figure_2.png", plot = figure_2, height = 10, width = 11)

```

Examine the corpus using tfidf and word counts.

```{r}
# Get word counts by document
corpus_counts <- tokenized_corpus %>% 
  count(filename, word) %>% 
  group_by(filename) %>% 
  mutate(total_words = n()) %>% 
  ungroup()

corpus_tfidf <- corpus_counts %>% 
  bind_tf_idf(word, filename, n)

corpus_tfidf %>% 
  arrange(desc(tf_idf)) %>% 
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  top_n(20) %>% 
  ggplot(aes(word, tf_idf, fill = filename)) +
  geom_col() +
  labs(x = NULL, y = "tf-idf") +
  coord_flip()

corpus_tfidf %>% 
  arrange(filename, desc(tf_idf)) %>% 
  group_by(filename) %>% 
  top_n(10, tf_idf) %>% 
  summarize(keywords = str_c(word, collapse = ", ")) 

corpus_tfidf %>% 
  filter(word %in% c("pawn", "weapon")) %>% 
  arrange(desc(tf_idf)) %>%
  top_n(20)
```

### Generating topic models

```{r}
## Topic models
set.seed(3452)
#We have to cast our data frame to a sparse matrix.

corpus_dtm <- corpus_counts %>% 
  filter(filename %in% sample_corpus$filename) %>% 
  cast_dtm(filename, word, n)

# Look at the dtm
corpus_dtm

corpus_dtm[1:6, 1:6] %>% as.matrix()

```
```{r}

#Creat LDA Corpora by differnt numbers of topics
corpus_lda <- LDA(corpus_dtm, k = 20, control = list(seed = 6432))
```


```{r}
# Creating and rds to save time

#saveRDS(wright_lda, "wright_sample_lda.rds")
#wright_lda <- readRDS("wright_sample_lda")

# if (!file.exists("corpus_lda.rds")) {
#  system.time({corpus_lda <- LDA(wright_dtm, k = 50, control = list(seed = 6432))})
#  saveRDS(corpus_lda, "wright_lda.rds")
# } else {
#  corpus_lda <- readRDS("corpus_lda.rds")
#}
```



```{r}
corpus_topics <- tidy(corpus_lda, matrix = "beta")

corpus_topics_display <- corpus_topics %>% 
  mutate(beta = round(beta, 4)) %>% 
  group_by(topic) %>% 
  top_n(15, beta) %>% 
  arrange(topic, desc(beta))

```



 
```{r}
corpus_topics_display %>% 
  group_by(topic) %>% 
  summarize(words = str_c(term, collapse = ", "))
```

```{r}
corpus_topics %>%
  group_by(topic) %>%
  top_n(12, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>% 
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

```{r}
#We can also get the association between documents and topics.

corpus_docs <- tidy(corpus_lda, matrix = "gamma")

corpus_docs %>% 
  mutate(gamma = round(gamma, 2)) %>% 
  group_by(topic) %>% 
  filter(gamma > 0.2) %>% 
  top_n(10, gamma) %>% 
  arrange(topic, desc(gamma))
```

```{r}
# Repeating the process with a different number of topics
corpus_lda2 <- LDA(corpus_dtm, k = 12, control = list(seed = 6432))

corpus_topics2 <- tidy(corpus_lda2, matrix = "beta")

corpus_topics_display2 <- corpus_topics2 %>% 
  mutate(beta = round(beta, 4)) %>% 
  group_by(topic) %>% 
  top_n(20, beta) %>% 
  arrange(topic, desc(beta))

corpus_topics_display2 %>% 
  group_by(topic)  
  # % summarize(words = str_c(term, collapse = ", "))

topic_labs <- c("1" = "1 - Apocalyptic/Prophecy", "2" = "2 - Treasure hunting","3" = "3 - Bladesmithing", "4" = "4 - Collecting/Cars", "5" = "5 - Space and Technology", "6" = "6 - Competition/Killing", "7" = "7 - Collecting/Antiques", "8" = "8 - American military", "9" = "9 - Mixed", "10" = "10 - Aliens", "11" = "11 - Classic Cars", "12" = "12 - Capitalism")

figure_1 <- corpus_topics2 %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>% 
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  labs(title="Topics on History") +
  theme(plot.title = element_text(hjust = 0.5, size = 18)) +
  theme(axis.title.y = element_text(size = 16)) +
  theme(axis.title.x = element_text(size = 16)) +
  theme(axis.title.x = element_text(margin = margin(t = 15, r = 00, b = 8, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 15))) +
  theme(plot.title = element_text(margin = margin(t = 15, r = 00, b = 15, l = 0))) +
  xlab("Terms") +
  ylab("Word Probability Per Topic") +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, nrow = 3, scales = "free", labeller=labeller(topic = topic_labs)) +
  coord_flip() 
```


```{r}
# Code to save output
 ggsave("figure_1.png", plot = figure_1, height = 9, width = 12)
```
  
